---
title: "FlavorAnalysis_official"
output: html_document
---
_Describe Content_
1. Import flavor text data
2. Import flavor tweet data
3. Describe content data

_Import Survey Data_
1. Apply survey weights
2. Keep recontact survey data

_Merge survey and content data_
1. Aggregate content data for text and twitter
2. Combine text, twitter, and survey data

_Create dataframe with necessary variables for analysis_
r <- clusterecontact0724
1. Standardize content measures
2. Generate binary belief measures
3. keep only date, belief measures, content measures, vaping experience, and age group 
```{r}
y<- r %>% select(bel_vap_taste2, taste_agree, vap_ever2, t2_age_bin2, tastetexts_28day, tastetweets_28day, sttastetexts_28day, sttastetweets_28day, lflevel_bin) 

```

_Describe main variables_
```{r}
summary(r$tastetexts_28day)
summary(r$tastetweets_28day)
summary(r$bel_vap_taste2)
mytable<-table(r$bel_vap_taste2)
prop.table(mytable)
mytable2<-table(r$vap_ever2)
prop.table(mytable2)
mytable3<-table(r$t2_age_bin2)
prop.table(mytable3)
```

_Correlations_
library(Hmisc)
```{r}
cor(y %>% select(sttastetexts_28day, sttastetweets_28day, bel_vap_taste2, vap_ever2, t2_age_bin2) %>% na.omit())

```
_Conduct Analyses_
1. Assess effects of content on belief
  a. ordinal logistic regression: main effects model (no interaction)
  b. ordinal logistic regression: interaction model 
  c. logistic regression with binary belief measure


```{r}
y$lflevel_bin <- factor(y$lflevel_bin)
mylogit <- glm(taste_agree ~ sttastetweets_28day + lflevel_bin + sttastetweets_28day * lflevel_bin  data = y)
mylogit
summary(mylogit)
confint(mylogit)
confint.default(mylogit)
exp(coef(mylogit))
exp(cbind(OR = coef(mylogit), confint(mylogit)))




newdata1 <- with (r, data.frame(sttastetweets_28day = mean(sttastetweets_28day), lflevel_bin = factor(0:1)))

newdata1$lflevel_binP <- predict(mylogit, newdata = newdata1, type = "response")
newdata1

summary(r$sttastetexts_28day)

newdata2 <- with(r, data.frame(sttastetweets_28day = rep(seq(from = -1, to = 4.5, length.out = .5),
    2), lflevel_bin= factor(rep(0:1, each = .5))))

newdata3 <- cbind(newdata2, predict(mylogit, newdata = newdata2, type = "link",
    se = TRUE))
newdata3 <- within(newdata3, {
    PredictedProb <- plogis(fit)
    LL <- plogis(fit - (1.96 * se.fit))
    UL <- plogis(fit + (1.96 * se.fit))
})

ggplot(mylogit, aes(x = r$sttastetweets_28day, y = PredictedProb)) + geom_ribbon(aes(ymin = LL,
    ymax = UL, fill = rank), alpha = 0.2) + geom_line(aes(colour = rank),
    size = 1)
```
2. Produce graph
  a. create high and low groups for content variables
  b. run analysis with groups
  c. predicted values graphs
  ##Jake's ggplot##
    ggplot(dataframe, aes(x = tweets, y= prop, colot = longform)) + geom_smooth(method='lm') + stat_summmary(fun.data='mean_cl_bloot', size =1) 
  
3. Other analyses
  a. age as potential moderator (ordinal logistic regression)
  b. vaping experience as potential moderator (ordinal logistic regression)
  c. sensitivity analyses for overall content on taste belief (ordinal logistic regression)
  d. sensitivity analyses for other beliefs (13 ordinal logistic regressions)
4. Content themes
  a. random sample selection
  b. import coded content
  c. table of proportions for each theme 




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
